\documentclass[11pt,a4paper]{article}
\title{\vspace{-6ex}\bfseries Ciprian Ioan Tomoiag\u{a}\vspace{-7ex}}
\date{\vspace{-5ex}}       %remove the space occupied by date
\usepackage[margin=1cm]{geometry}

\setlength{\parskip}{0.15in}

%packages for email
\usepackage{hyperref}
\usepackage{url}

% new package for easier tables
\usepackage{tabu}
\usepackage{longtable}

\begin{document}
\maketitle
\thispagestyle{empty}

%heading: Address and contact
\begin{center}
1, Brownslow walk, Manchester, UK, M13 9UQ

Email: ciprian.tomoiaga@gmail.com; Mobile: +44 (0) 774 6373 029\vspace{-2ex}
\end{center}

\section*{Education\vspace{-2ex}}

% \begin {tabu} to <desired_width> {X[width, align, type]}
\begin {tabu} to\linewidth {X[0.14, r, p]X[0.8, j, p]}

\bf 2012--2016&{\bf The University of Manchester}\\
& BSc (Hons) Computer Science with Industrial Experience\\
& Expected result: 1\textsuperscript{st} Class (First year average: 81\%)\vspace{5pt}\\
& Achieved extensive programming experience with web development technologies and 
several programming languages, including Java, Python, ARM assembly and 
shell scripting. Gained familiarity with basic computer science concepts such as
Artificial Intelligence, Distributed Systems, Computer Engineering and Computer Architecture.\vspace{10pt}\\

\bf 2008--2012 & \bf"Liviu Rebreanu" National College, Bistrita, Romania\\ 
& Baccalaureate exam (9.41/10 average):\\
& Mathematics (9.5/10), Computing (9.3/10), Literature (9.45/10)\vspace{5pt}\\
& Graduation average: 9.91/10\vspace{5pt}\\
& Developed excellent practical programming knowledge in various computer 
languages (C\#, C, C++, PHP) and computer science fields (algorithms, relational
 databases, web development), as well as good coding practices.\\
\savetabu {tom}   % use the same tabu multiple times
\end{tabu}

\vspace{-2ex}

\section*{Relevant work experience\vspace{-2ex}}

\begin {longtabu} to\linewidth {X[0.15, r, p]X[0.8, j, p]}

\bf June--August & \bf Summer Intern at Codemart\\
\bf 2013 & Worked on an international neuroscience research project, The Virtual Brain, where I 
solved bugs and developed several new functionalities.
My tasks included assessing and improving performance of existing code and 
devising new methods for visualising big brain data. I also had to solve the 
challenge of implementing them for the web, using WebGL and JavaScript.\vspace{5pt}\\
& As a result, I improved my overall coding skills and gained familiarity with industry tools and 
concepts such as issue tracking and version control.\vspace{10pt}\\

\bf March--May & \bf First year team project\\
\bf 2013 & Designed and built from scratch a movie review website, along with a team of 6. 
Used only open source technologies and no helping frameworks to get a good, 
low level, understanding of how the internet and the web works.\vspace{5pt}\\
& Proved very good team working abilities and improved on my web development skills.\vspace{10pt}\\

& \bf Basic chat client\\
& Designed a chat protocol and implemented the related client-server 
architecture to teach myself better Python and GUI programming.\vspace{10pt}\\

\bf 2011--2012 & \bf Application developer in C\#\vspace{5pt}\\

& \hspace{1em}$\circ$\hspace{1.5em}
Designed and developed an application used by a genetics PhD for selecting, 
merging and analysing relevant features from a huge amount of data. It reduced 
user's working time from a few weeks to a few days.\vspace{5pt}\\

& \hspace{1em}$\circ$\hspace{1.5em}
Designed and developed an application for a driving school which generated tests 
for the users and kept track of their progress.\vspace{5pt}\\

& \hspace{1em}$\circ$\hspace{1.5em}Designed and developed an online shop for my 
high school final year project with different functionalities for the buyer 
(categorising, sorting and searching) and for the administrator (adding, 
removing and editing items and offering promotions).\vspace{5pt}\\
&Achieved solid practical skills using C\#, .Net, ASP and MySQL in software 
development and gained familiarity with the Visual Studio IDE.\vspace{5pt}\\

\end{longtabu}

\vspace{1.3em}    % white space to force a new page

\section*{Other work experience\vspace{-2ex}}

\begin {tabu} {\usetabu{tom}} % use a previously saved tabu

\bf June--July & \bf Balkan Olympiad in Informatics\\
\bf 2011 & Volunteered in organising the Balkan Olympiad in Informatics.\vspace{5pt}\\
& Demonstrated very good communication and organisation abilities, as the chief 
of the Media department, where I coordinated a team of 5 in writing newsletters 
and magazines, taking interviews and facilitating translations of tasks. Also, 
proved excellent organisational and leadership skills, being coordinator of more 
than 20 guides, each of them being responsible of a country's team.\vspace{5pt}\\

\bf 2009--2011
& \textbf{Summer and part time job} as both bartender and supervisor at a local 
pub. Apart from dealing promptly, efficiently and in a friendly manner with 
customers' requests, my duties included managing events, staff, expenses and 
promotions, which produced a revenue increase of approximately 20\%. \vspace{5pt}\\

& Developed excellent leadership and supervisory abilities, as well as marketing 
skills and commercial awareness.\vspace{5pt}\\

\bf 2010--2012 &
\textbf{Volunteering} in environmental campaigns and organisations like "Let's 
do it, Romania!" and Greenpeace.\vspace{5pt}\\

& Gained team work experience and environmental awareness.\\
\end{tabu}

\vspace{-2ex}

\section*{Achievements and Awards\vspace{-2ex}}

\begin {tabu} {\usetabu{tom}} % use a previously saved tabu

\bf 2013 & \bf University of Manchester GameJam Hackathon\\
& My team won the prize for "Most original game idea"\vspace{5pt}\\

\bf 2009--2012
& Constantly ranked in top 3 at county and inter-county rounds of national contests
in Physics, Maths and Computing, including the Romanian National Olympiad in each.\vspace{5pt}\\
& Demonstrated self education and research skills, as these achievements were 
gained mostly through self study in my own spare time, as well as good time management.\\ 
\end{tabu}

\vspace{-2ex}

\section*{Additional skills and qualifications\vspace{-2ex}}

\begin {tabu} {\usetabu{tom}} % use a previously saved tabu
\bf IELTS & Scored 8/9 at the IELTS Academic Module\vspace{5pt}\\
\bf IT & \textbf{Applications:} typesetting in \LaTeX, Proficient in Microsoft Office; 
graphic \& vectorial image processing in Adobe Photoshop and Corel Draw\\
& \textbf{Programming:} C, C++, Java, Python, C\#, PHP, JavaScript, WebGL, ASP .NET, MySQL\vspace{5pt}\\
\bf Driving & Full clean driving licence\\
\end{tabu}

\vspace{-2ex}

\section*{Interests and Activities\vspace{-2ex}}

\begin {tabu} {\usetabu{tom}} % use a previously saved tabu

\bf Competing & Taking part in programming contests (Facebook HackerCup, Google 
Codejam, TopCoder SRMs) and hackathons (Microsoft WOWZAPP, UoM Gamejam) to gain 
new skills, develop on existing ones and keep my motivation high.\\
\bf Sports & Member of dancing societies, and enjoy participating in meetings 
and dance workshops, to relax and develop creativity. Also, regularly swim and 
work out to keep myself fit and healthy.\\
\end{tabu}
\thispagestyle{empty}

\end{document}
